From Principles to Fashion with Class

### 2013-04-12 tfpie/tfpie.tex
Makefile and rename.
Some leg work on references.

\documentclass[submission,copyright]{eptcs}
\providecommand{\event}{TFPIE} % Name of the event you are submitting to
\usepackage{breakurl}             % Not needed if you use pdflatex only.

\title{How to Design Programs with Class}
\author{Sam Tobin-Hochstadt \quad\qquad David Van Horn
\institute{Northeastern University\\
Boston, Massachusetts, USA}
\email{\{samth,dvanhorn\}@ccs.neu.edu}
}
\def\titlerunning{A Longtitled Paper}
\def\authorrunning{S. Tobin-Hochstadt \& D. Van Horn}
\begin{document}
\maketitle

@@

@@

\section{Distributed, Interactive Programs}

\section{Representation-indepence and interface-oriented programming}

\section{Unifying functions and objects}

@@

@@

Some of these are premature, and better introduced later in the
course.  Some are just irrelevant trivia (different syntax) that often
favors ``experienced'' students while needlessly intimidating students
with only the previous semester under their belt.  Many of these
trivial matters, e.g. Eclipse configuration, javac command line
arguments, the CLASSPATH, can be very frustrating to the uninitiated,
causing students to believe struggling with such crap is \emph{the
  essence of computer science}.  Bright, promising students

@@

\nocite{*}
\bibliographystyle{eptcs}
\bibliography{generic}
\end{document}

>>>>

\documentclass[submission,copyright]{eptcs}
\providecommand{\event}{TFPIE} % Name of the event you are submitting to

\title{From Principles to Fashion with Class}
\author{Sam Tobin-Hochstadt \quad\qquad David Van Horn
\institute{Northeastern University\\
Boston, Massachusetts, USA}
\email{\{samth,dvanhorn\}@ccs.neu.edu}
}
\def\titlerunning{A Longtitled Paper}
\def\authorrunning{S. Tobin-Hochstadt \& D. Van Horn}
\begin{document}
\maketitle

@@

\cite{dvanhorn:Felleisen2004Structure}

\cite{dvanhorn:Findler2002DrScheme}

\cite{dvanhorn:Felleisen2001How}

@@

\section{Our course}

\subsection{Distributed, Interactive Programs}

\subsection{Representation-indepence and interface-oriented programming}

\subsection{Unifying functions and objects}

@@

\cite{dvanhorn:Gray2003ProfessorJ}

\cite{dvanhorn:Allen2002DrJava}

\cite{dvanhorn:Kolling2003}

@@

Some of these are premature, and better introduced later in the
course.  Some are just irrelevant trivia (different syntax) that often
favors ``experienced'' students while needlessly intimidating students
with only the previous semester under their belt.  Many of these
trivial matters, e.g. Eclipse configuration, javac command line
arguments, the CLASSPATH, can be very frustrating to the uninitiated,
causing students to believe struggling with such crap is \emph{the
  essence of computer science}.  Bright, promising students may leave
the program, understandably so, in order to pursue more intellectually
fulfilling subjects.

@@

% \nocite{*}
\bibliographystyle{eptcs}
\bibliography{dvh-bibliography}
\end{document}
